Issues with Dynamical Measurements Across the Disk

### 2019-02-17 paper/ms.tex
Update citations in first paragraph

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the
era of {\em Gaia} DR2. Recent major discoveries include the remnants of a
major merger \citep{2018Natur.563...85H}, a phase-space spiral (\Gus{cites})
indicating local substructure infall (\Gus{cites}), a gap indicative of a dark
matter subtructure in GD1 \citep{2018arXiv181103631B}, and \Gus{others}.

>>>>

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the
era of {\em Gaia} DR2. Recent major discoveries include the remnants of a
major merger
\citep{2018ApJ...860L..11K,2018Natur.563...85H,2018arXiv180704290L,2019MNRAS.482.3426M},
a phase-space spiral \citep{2018Natur.561..360A} indicating either local
substructure infall \citep{2018MNRAS.481.1501B,2018arXiv180800451L} or bar
buckling \citep{2018arXiv181109205K}, a gap indicative of a dark matter
subtructure in GD1 \citep{2018arXiv181103631B}, among others.
